% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

CAMERON BROOKS

London, ON · (647)331-4074

\textbf{cbrook49@uwo.ca ·
      \href{https://www.linkedin.com/in/Cameron-Brooks-CB/}{linkedin.com/in/Cameron-Brooks-CB}
      ·
      \href{https://www.appropedia.org/User:CameronBrooks11}{appropedia.org/User:CameronBrooks11}}

\textbf{\uline{Profile}}

Electrical engineering student with technical and leadership experience
in various employment, volunteer, and extracurricular positions. I
engage in engineering research and development across various fields,
and I have a passion for social entrepreneurship.

\textbf{\uline{Key Qualifications}}

\begin{itemize}
      \item
      \item
            Literature Review \& Academic Paper Writing
      \item
            Systems Thinking and Design
      \item
            CAD (FreeCAD, Fusion360, Onshape)
      \item
            Development Utilities (Git, WSL, IDE)
      \item
            Spreadsheet \& Document Preparation
      \item
            Electric Circuit Prototyping and Design
      \item
            Google and Microsoft workspace
      \item
            Microcontroller Programming
      \item
            Power Electronics
      \item
            3D Printing
      \item
            Object-Oriented Programming
\end{itemize}

\textbf{\uline{Relevant Experience}}

\textbf{Technical Research Support Associate -- Department of Electrical
      \& Computer Engineering}

Nov. 2021 -- Present \textbar{} Western University, London, ON, Canada

\begin{itemize}
      \item
            \href{https://www.appropedia.org/User:CameronBrooks11}{Lead
                  investigator} for multiple research projects spanning the areas of
            hardware development, resistive heating, plastic recycling, 3D
            printing and sanitization.
      \item
            Many of my projects are a direct or indirectly contribution to
            research involving the conversion of waste plastics into alternative
            food in collaboration with the \href{https://www.darpa.mil/}{Defense
                  Advanced Research Projects Agency (DARPA).}
      \item
            My main project currently is researching hypochlorite production via
            membrane-less microfluidic electrolysis.
      \item
            Research associate under the supervision of
            \href{https://www.eng.uwo.ca/electrical/faculty/pearce_j/index.html}{Dr.
                  Joshua Pearce} as part of the
            \href{https://www.appropedia.org/Category:FAST}{Free Appropriate
                  Sustainable Technology (FAST) Research Group} in the Faculty of
            Engineering and member of the Institute for Earth and Space
            Exploration.
\end{itemize}

\textbf{Teaching Associate -- How to Change the World Organization}

Feb. 2023 (contract); Nov. 2022 (contract); Nov. 2021 (participant)
\textbar{} Global/London, ON, Canada

\begin{itemize}
      \item
            Guide and advise students as they create an action plan to address
            their given \href{https://www.htctw.org}{HtCtW} challenge SDG 6
            (\href{https://www.un.org/sustainabledevelopment/water-and-sanitation/}{Access
                  to Water and Sanitation}) in Thunder Bay, Ontario.
      \item
            I was previously a program participant where my group developed and
            proposed an action plan for
            \href{https://www.appropedia.org/Nets_for_Uganda:_Local_Manufacturing_for_Malaria_Prevention}{malaria
                  prevention in rural Uganda} that we then
            \href{https://www.appropedia.org/Nets_for_Uganda:_Local_Manufacturing_for_Malaria_Prevention}{published
                  online.}
\end{itemize}

\textbf{Vice-President Internal -- Undergraduate Engineering Society}

April 2023 -- April 2024; March 2021 -- April 2022; April 2022 --
Present \textbar{} Western University, London, ON, Canada

\begin{itemize}
      \item
            The Vice-President Internal for the 2023-24 academic year.
      \item
            As previous Wellness Commissioner, I was responsible for
            \href{https://wellnessforce.wixsite.com/website}{Wellness Force} and
            chairs all Wellness Force meetings for the year as well as promoting
            student wellness through the planning of events, providing resources,
            and creating initiatives.
      \item
            I was previously the sustainability coordinator for the
            \href{https://sustainability.uwo.ca/get_involved/join_a_office/index.html}{Sustainability
                  Committee} where I my primary role was to track and minimize the
            environmental footprint of the Undergraduate Engineering Society.
\end{itemize}

\textbf{Student Ambassador -- Engineering Recruitment and Outreach}

Oct. 2022 -- Present (volunteer) \textbar{} Western University, London,
ON, Canada

\begin{itemize}
      \item
            Student Ambassadors are students with first-hand experience with the
            various aspects of undergraduate engineering at Western University
            such as co-op, programs, research, clubs and teams, and anything else
            related.
\end{itemize}

Student Ambassadors run informative Q\&As and appear in profiles to
provide information about their experiences.

\textbf{Volunteer Engineering Intern -- Field Ready}

Jan. 2022 -- Jan. 2023 (volunteer) \textbar{} Global/Remote

\begin{itemize}
      \item
            My primary focus was with the Rapid Response Manufacturing project
            based in Fiji and will be deployed in the
            \href{https://www.fieldready.org/emergencies}{South Pacific}.
      \item
            To further develop the capabilities of the team and its members I am
            assisting with a memorandum of understanding with Western University
            whereby Field Ready employees can get advanced degrees in their field
            while continuing their work.
\end{itemize}

\textbf{Swimming and Lifesaving Instructor -- Self-Employed}

June 2020 -- Aug. 2020 (self-employed); April 2021 -- Aug. 2021
(self-employed) \textbar{} Uxbridge, ON, Canada

\begin{itemize}
      \item
            I managed and instructed my own private, at-home aquatics lessons
            business geared towards busy high-end clientele.
      \item
            This entrepreneurial endeavour allowed me to leverage my previous
            training in aquatics and first response to teach the swim kids program
            as well as the Bronze Lifesaving Awards in accordance with Red Cross
            standards.
\end{itemize}

\textbf{\uline{Education}}

\textbf{University of Western Ontario}

\begin{itemize}
      \item
            Bachelor of Engineering Science -
            \href{https://www.eng.uwo.ca/undergraduate/programs/electrical.html}{Electrical
                  Engineering} (BESc `24)
      \item
            Key courses: Design, Electric Circuits, Object-Oriented Programming,
            Digital Logic, Microcontrollers, Economics, Electromagnetics
      \item
            Progression: Year 1 Medical Sci. (2020/21), Year 2 Electrical Eng.
            (2021/22), Year 3 Electrical Eng. (2022/23)
\end{itemize}

\textbf{\uline{Awards and Honours}}

\begin{itemize}
      \item
            \href{https://www.zenithpathways.ca/}{Zenith Canada Pathways
                  Foundation} Space Fellowship Mentee 2023
      \item
            \href{https://www.ieee.org/}{Institute of Electrical and Electronics
                  Engineers}, Student Member 2021-2023
            (\href{https://cis.ieee.org/activities/membership-activities/ieee-member-directory}{98525168})
      \item
            Ontario Professional Engineers Foundation for
            \href{https://engineersfoundation.ca/}{Education Scholarship} 2022
      \item
            Bill \& Barbara Etherington
            \href{https://www.eng.uwo.ca/graduate/funding/nserc-usra.html}{Fellowship
                  Award} 2022
      \item
            Ezz Amr Prize for Most Feasible
            \href{https://www.westerniec.com/}{Business Pitch 2021}
      \item
            Western University
            \href{https://registrar.uwo.ca/student_finances/scholarships_awards/admission/western_admission_scholarship_program.html}{Scholarship
                  of Distinction} 2020
      \item
            Certificate of
            \href{https://www.ddsb.ca/en/programs-and-learning/programs-and-learning-french-immersion.aspx\#Uxbridge}{French
                  Immersion Studies} 2020
      \item
            \href{https://schulichleaders.com/}{Schulich Leader} Nominee 2019
\end{itemize}

\textbf{\uline{Projects and Written Works}}

\textbf{FAST Research Group}

\emph{Additive Manufacture Breakout Boards (AMBB) {[}complete{]}}

\begin{itemize}
      \item
            Electronic designers are constantly faced with shortages and
            incompatibilities, to address this I created a parametric 3D printable
            device that allows conversion between chip packages, is reusable, and
            costs 88\% less than traditional methods.
      \item
            My findings were compiled into an \href{https://osf.io/t87ks}{academic
                  paper} that is currently under review to be published in
            \emph{Inventions} which includes the full technical specifications,
            device validation, economic analysis, and discussion for future work.
\end{itemize}

\emph{Hypochlorous Acid Generator {[}in-progress{]}}

\begin{itemize}
      \item
            To address the global need for safe, cost-effective sanitization I am
            designing an open-source device that can produce hypochlorous acid, a
            powerful disinfectant, via membrane-less microfluidic electrolysis.
            This will give individuals and institutions with limited resources
            access effective sanitization that is safe, cost effective, and
            locally produced.
\end{itemize}

\emph{Resistive Heating Elements and Controls {[}multiple ongoing
projects{]}}

\begin{itemize}
      \item
            This multi-project initiative aims to reduce costs and improve
            efficiency of systems requiring resistive heating through use of off
            the shelf parts such as microcontrollers and high-temperature wire to
            create custom heating solutions.
      \item
            Main applications currently include an industrial sheet press for
            plastic recycling and a bioreactor for pyrolysis.
\end{itemize}

\textbf{University of Western Ontario}

\emph{ECE 2240A Final Project {[}complete{]}}

\begin{itemize}
      \item
            The purpose of
            \href{https://drive.google.com/file/d/1An5rJPhcd0g3xI0Vsjve0MKh0RhyBITk/view?usp=sharing}{this
                  project} was to apply our knowledge of circuit design and simulation
            software (microcap, EAGLE) to design a circuit, and then implement it
            using appropriate components to make a function generator.
\end{itemize}

\emph{ECE 2231A Final Report {[}complete{]}}

\begin{itemize}
      \item
            \href{file:///G:/Applications/Resumes/•\%09https:/drive.google.com/file/d/17ikyDcy2dAAxGbxkXLpNu5Zhl9YPJUlv/view\%3fusp=sharing}{This
                  report} describes the current-voltage characteristic of the Zener
            diode through theoretical discussion as well as analysis of
            experimentally obtained data.
\end{itemize}

\emph{ECE 2242A Final Project {[}complete{]}}

\begin{itemize}
      \item
            The purpose of
            \href{file:///G:/Applications/Resumes/•\%09https:/drive.google.com/file/d/1vDwskj48cE9Amr8lPI0j0d2goCWOxL-1/view\%3fusp=sharing}{this
                  project} was to apply our knowledge of microcontrollers and
            electronics prototyping to design a solution to a real-world problem.
            We designed \emph{The AutoMorn} to streamline and improve the morning
            routine of students.
\end{itemize}

\end{document}
